Evaluating Jaccard Index Between Annotations

### 2019-05-14 Scripts/calculating_jaccard_index_between_annotations.Rmd
editted results script

####All
```{r}
jaccard.mat.gm12878 <- readRDS("Z:/TAD_data_analysis/jaccard/jaccard.mat.gm12878.rds")
jaccard.mat.gm12878 <- jaccard.mat.gm12878[!duplicated(rownames(jaccard.mat.gm12878)), !duplicated(colnames(jaccard.mat.gm12878))]

corrplot(jaccard.mat.gm12878, method = "square",
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .4,
         col=colorRampPalette(c("white", "red"))(100),
         cl.pos="n",
         mar = c(0, 0, 0, 0))
```

@@

>>>>

```{r}
jaccard.mat.gm12878 <- readRDS("Z:/TAD_data_analysis/jaccard/jaccard.mat.gm12878.rds")
jaccard.mat.gm12878 <- jaccard.mat.gm12878[!duplicated(rownames(jaccard.mat.gm12878)), !duplicated(colnames(jaccard.mat.gm12878))]

@@

####All

```{r}
corrplot(jaccard.mat.gm12878, method = "square",
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .4,
         col=colorRampPalette(c("white", "red"))(100),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

all_melted_gm12878 <- rbind.data.frame(melted_css,
                                       melted_hm,
                                       melted_tfbs)
all_melted_gm12878$annotation <- c(rep("CSS", length(melted_css$Var1)),
                                   rep("HM", length(melted_hm$Var1)),
                                   rep("TFBS", length(melted_tfbs$Var1)))
all_melted_gm12878$annotation <- factor(all_melted_gm12878$annotation, levels=c("CSS", "HM", "TFBS"))

ggplot(all_melted_gm12878[-which(all_melted_gm12878$annotation=="CSS"),], aes(x=value, group=annotation, color=annotation)) + 
  geom_density(size=1) +
  xlim(0,1) +
  xlab("Jaccard Index") +
  ylab("Density") +
  scale_color_discrete(name="Annotation Group") +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
     axis.text.y = element_text(size=15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))
```
